---
output: latex_fragment
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: apa.csl
---

```{r setup, include=FALSE}
# R Studio Clean-Up
cat("\014") # clear console
# rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
gc() # garbage collector

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
lib <- c(
  "rmarkdown",
  "knitr",
  "remedy",
  "bookdown",
  "brms",
  "psych",
  "ggplot2",
  "ggthemes",
  "haven",
  "RColorBrewer",
  "plotly",
  "gridExtra",
  "ggpattern",
  "lme4",
  "nlme",
  "jtools",
  "gtsummary",
  "sessioninfo",
  "tibble",
  "pander",
  "devtools",
  "mada",
  "data.table",
  "plyr",
  "dplyr",
  "tidyr",
  "Hmisc",
  "kableExtra",
  "papaja",
  "stringr",
  "stringi",
  "reshape2",
  "lubridate"
)
invisible(lapply(lib, library, character.only = TRUE))
rm(lib)

# Load Custom Packages
source("./scripts/functions/fun.panel.R")
source("./scripts/functions/themes.R")
source("./scripts/functions/binaryCor.R")

# Markdown Options
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # set working directory
knitr::opts_knit$get("root.dir") # check working directory
options(
  scipen = 999,
  digits = 4,
  width = 400
) # removes scientific quotation
# knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings

# Global Chunk Options
knitr::opts_chunk$set(
  fig.width = 12,
  fig.height = 8,
  fig.path = "Figures/",
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
```

```{r import, include=FALSE}
load("data/wrangled.RData")
```

\faQuestionCircle\ Unsure about order of study one and two. Currently chronological. But could also be: (1) main model works in larger student sample, (2) works in economic migrant sample, (3) test full thing in medical sample.

\section{Study 1}

Based on our main hypotheses, the aim of our first study is to specifically test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts. To this aim, we conducted an intensive longitudinal survey study with recent migrants to the Netherlands, gathering a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations. Data was collected from May 5th through June 6th, 2018 (and all participants started the study within the first two days).

The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B.

\subsection{Methods}

```{r workerSampleInfo, include=FALSE}
# combine education measure
workerOccupation <- 
  dtWorker$clean %>%
  select(PID, starts_with("occupation")) %>%
  mutate_all(as_factor) %>% 
  mutate_all(as.character) %>%
  replace(is.na(.), "") %>%
  unite("occupation", -PID, sep = "/") %>%
  mutate(occupation = trimws(occupation, which = "both", whitespace = "[/]")) %>%
  distinct

# summarize participant characteristics
workerSampleInfo <- 
  dtWorker$clean %>%
  group_by(PID) %>%
  summarise(
    dailiesN = n(), 
    age = age,
    gender = as_factor(Gender),
    edu = as_factor(education_level),
    nationality = as_factor(nationality)
  ) %>%
  distinct

# add occupation variable
workerSampleInfo <- merge(workerSampleInfo, workerOccupation)
rm(workerOccupation)

# look at frequencies of characteristics 
table(workerSampleInfo$gender)
table(workerSampleInfo$edu)
table(workerSampleInfo$occupation)
table(as.character(workerSampleInfo$nationality))
```


\subsubsection{Participants} After receiving ethical approval from the University of Groningen, we recruited `r nrow(workerSampleInfo)` migrants using the local paid participant pool and specifically targeted non-Dutch migrants to participate in our study. Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon). With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{M} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r sum(workerSampleInfo$dailiesN)`). This is a common number of measurements found in experience sampling studies and should offer sufficient power to model processes within and between participants \citep[e.g., for a systematic review see][]{AanhetRot2012}. Participants were compensated for their participation with up to 34 Euros – each two Euros for pre- and post-questionnaire as well as 50 Eurocents for every experience sampling measurement occasion. The sample consisted of relatively young, educated, and western migrants from the global north ($M_{age}$ = `r format(round(mean(workerSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(workerSampleInfo$age),2), nsmall=2)`, `r nrow(workerSampleInfo %>% filter(gender == "Female"))` women, `r nrow(workerSampleInfo %>% filter(occupation == "student"))` students). The sample accurately describes one of the largest groups of migrants in the region \citep[][]{GemeenteGroningen2015}.

\subsubsection{Procedure} The study itself consisted of three main parts, an introductory pre-measurement, and the daily experience sampling measurements, as well as a concluding post-measurement. After giving informed consent, participants started by filling in an online pre-questionnaire assessing demographics and general information about their immigration. Over the next thirty days, the participants then were invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_))`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_)))`). After the final day of daily diary measurements, participants were invited to fill in a longer post measurement survey that mirrored the pre-measurement. All key variables in for this study were part of the short daily diary surveys. 

\subsubsection{Materials}

\subsubsubsection{Intergroup Contact} 
To test the prerequisite effect of intergroup contact, every ‘Experience Recap’ started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}” 

\subsection{Results}

\section{Study 2}

\subsection{Methods}

\subsection{Results}

\section{Study 2}

\subsection{Methods}

\subsection{Results}

<!-- \begin{figure}[h] -->

<!-- \centering -->

<!-- \caption{PRISMA Diagrams for the Theoretical, Methodological, and Empirical Literature.} -->

<!-- \makebox[\textwidth]{\includegraphics[width=\paperwidth]{Figures/PrismaCombined}} -->

<!-- \label{fig:PrismaCombined} -->

<!-- \end{figure} -->

<!-- \input{Tables/ExclusionsCombined} -->

<!-- \input{Tables/TheoreticalExclusion} -->

<!-- \begin{figure}[h] -->

<!-- \centering -->

<!-- \caption{Literature Levels: (A) Bar graph of the experience aspect frequencies for theoretical, methodological, and broader empirical literature. (B) Bar graph of the number of experience aspects used for theoretical, methodological, and broader empirical literature. (C) Average number of additional aspects included when the aspect was considered for theoretical, methodological, and broader empirical literature [Mean ± 95\%CI].} -->

<!-- \includegraphics[width=\textwidth]{Figures/LiteratureComparison-1} -->

<!-- \caption*{Note that in (C) within each literature body the aspects are not mutually exclusive (and thus not independent) because scales can include multiple experience aspects.} -->

<!-- \label{fig:LiteratureComparison} -->

<!-- \end{figure} -->
