---
title: "Supplemental Information B: Full Annotated Analysis and Reproducible Code"
subtitle: "Suppplemental Material for 'Psychological Needs During Intergroup Contact [working title]'"
author:
- Jannis Kreienkamp^1,2^
- Maximilian Agostini^1,2^
- Laura Bringmann^1,2^
- Peter de Jonge^1,2^
- Kai Epstude^1,2^
- ^1^University of Groningen, Department of Psychology
- ^2^Author order to be discussed; currently alphabetic by last name
- "Author Information:"
- "Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).  E-mail: <a href='mailto:j.kreienkamp@rug.nl'>j.kreienkamp@rug.nl</a>"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io" target="_blank">OSF link goes here</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://janniscodes.github.io/intergroup-contact-needs/" target="_blank">janniscodes.github.io/intergroup-contact-needs/</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: apa.csl
---

<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
.table {
  margin-left:auto; 
  margin-right:auto;
}
</style>


```{r setup, include=FALSE}
# R Studio Clean-Up
  cat("\014") # clear console
  #rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
  gc() # garbage collector
  
# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file 
lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra",
         "sessioninfo", "tibble", "pander", "devtools",
         "data.table", "plyr", "dplyr", "tidyr", "Hmisc", "kableExtra", 
         "stringr", "stringi", "reshape2", "lubridate")
invisible(lapply(lib, library, character.only = TRUE))  
rm(lib)  

# Load Custom Packages  
  source("./scripts/functions/fun.panel.R")
  source("./scripts/functions/themes.R")
  source("./scripts/functions/binaryCor.R")

# Markdown Options
  knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # set working directory
  knitr::opts_knit$get("root.dir") # check working directory
  options(scipen = 999, digits = 4, width = 400) #removes scientific quotation
  #knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings
  knitr::knit_hooks$set(
   error = function(x, options) {
     paste('\n\n<div class="alert alert-danger">',
           gsub('##', '\n', gsub('^##\ Error', '**Error**', x)),
           '</div>', sep = '\n')
   },
   warning = function(x, options) {
     paste('\n\n<div class="alert alert-warning">',
           gsub('##', '\n', gsub('^##\ Warning:', '**Warning**', x)),
           '</div>', sep = '\n')
   },
   message = function(x, options) {
     paste('\n\n<div class="alert alert-info">',
           gsub('##', '\n', x),
           '</div>', sep = '\n')
   }
  )
  htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# Global Chunk Options
  knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figures/',
                        echo=TRUE, warning=FALSE, message=FALSE)
```

<br/>

Note. Boxplots display the interquartile range (IQR, center box), and the whiskers extend 1.5*IQR from the lower and upper hinge. The white point indicates the mean and the white center line indicates the median.   

<br/>

# **Data Preparation**  

## Data Import  

```{r formrImport}
# workers
# initial data cleaning was done in SPSS (syntax files are available in "")
dtWorker <- list(
  raw.pre = read_spss("data/S1_Workers/processed/cleaned/MT - Pre-Measure - 06-15-2018.sav"),
  raw.post = read_spss("data/S1_Workers/processed/cleaned/MT - Post-Measure - 06-15-2018.sav"),
  raw.morning = read_spss("data/S1_Workers/processed/cleaned/MT - Morning - 06-15-2018.sav"),
  raw.afternoon = read_spss("data/S1_Workers/processed/cleaned/MT - Afternoon - 06-15-2018.sav")
)

# students
dtStudents <- list(
  raw.pre = read.csv(file = "data/S2_Students/raw/AOTS_Pre.csv", header = T, sep = ","),
  raw.post = read.csv(file = "data/S2_Students/raw/AOTS_Post.csv", header = T, sep = ","),
  raw.daily = read.csv(file = "data/S2_Students/raw/AOTS_Daily.csv", header = T, sep = ",")
)

# young medical professionals
dtMedical <- list(
  raw.pre = c(),
  raw.post = c(),
  raw.daily = c()
)

```

## Data Cleaning & Data Exclusions  

```{r cleanWorker}
#  important names for Morning and Afternoon
  names.m <- c(
    "StartDate",
    "EndDate",
    "Finished",
    "Duration__in_seconds_",
    "RecordedDate",
    "ExternalReference",
    "Meta_Operating_System",
    "Contact_dum",
    "number",
    "time",
    "duration_1",
    "dyad.group",
    "gr_size",
    "gr_type_1",
    "gr_type_2",
    "gr_type_3",
    "gr_type_4",
    "gr_type_5",
    "gr_type_6",
    "gr_type_7",
    "gr_type_8",
    "gr_type_9",
    "gr_type_10",
    "gr_type_11",
    "gr_type_12",
    "gr_type_13",
    "gr_type_14",
    "gr_type_15",
    "gr_type_16",
    "gr_type_17_TEXT",
    "gr_context_1",
    "gr_context_2",
    "gr_context_3",
    "gr_context_4",
    "gr_context_5",
    "gr_context_6",
    "gr_context_7",
    "gr_context_8",
    "gr_context_9",
    "gr_context_10",
    "gr_context_11",
    "gr_context_12",
    "gr_context_13_TEXT",
    "gr_context_14_TEXT",
    "gr_dutchness",
    "dyad_type_1",
    "dyad_type_2",
    "dyad_type_3",
    "dyad_type_4",
    "dyad_type_5",
    "dyad_type_6",
    "dyad_type_7",
    "dyad_type_8",
    "dyad_type_9",
    "dyad_type_10",
    "dyad_type_11",
    "dyad_type_12",
    "dyad_type_13",
    "dyad_type_14",
    "dyad_type_15",
    "dyad_type_16",
    "dyad_type_17_TEXT",
    "Context_1",
    "Context_2",
    "Context_3",
    "Context_4",
    "Context_5",
    "Context_6",
    "Context_7",
    "Context_8",
    "Context_9",
    "Context_10",
    "Context_11",
    "Context_12",
    "Context_13_TEXT",
    "Context_14_TEXT",
    "keyMotive",
    "keymotive_fulfillemt_1",
    "keyMotive_Dutch_1",
    "autonomy_1",
    "competence_1",
    "relatedness_self_1",
    "relatedness_other_1",
    "qualityAccidental_1",
    "qualityVoluntary_1",
    "qualityCooperative_1",
    "qualityDutchy_1",
    "quality_overall_1",
    "quality_meaning_1",
    "quality_star_1",
    "wantInt",
    "desire_type_1",
    "desire_type_2",
    "desire_type_3",
    "desire_type_4",
    "desire_type_5",
    "desire_type_6",
    "desire_type_7",
    "desire_type_8",
    "desire_type_9",
    "desire_type_10",
    "desire_type_11",
    "desire_type_12",
    "desire_type_13",
    "desire_type_14",
    "desire_type_15",
    "desire_type_16",
    "desire_type_17_TEXT",
    "desire_context_1",
    "desire_context_2",
    "desire_context_3",
    "desire_context_4",
    "desire_context_5",
    "desire_context_6",
    "desire_context_7",
    "desire_context_8",
    "desire_context_9",
    "desire_context_10",
    "desire_context_11",
    "desire_context_12",
    "desire_context_13_TEXT",
    "desire_context_14_TEXT",
    "Reason_nodesire",
    "keyMotive_noInt",
    "keyMotive_noInt_fulf_1",
    "autonomy_NoInt_1",
    "competence_NoInt_1",
    "relatedness_1_NoInt_1",
    "thermometerDutch_1",
    "thermometerDutchInt_2",
    "ExWB_1",
    "alertness1",
    "calmness1",
    "valence1",
    "alertness2",
    "calmness2",
    "valence2",
    "inNonDutch",
    "NonDutchNum",
    "NonDutchType_1",
    "NonDutchType_2",
    "NonDutchType_3",
    "NonDutchType_4",
    "NonDutchType_5",
    "NonDutchType_6",
    "NonDutchType_7",
    "NonDutchType_8",
    "NonDutchType_9",
    "NonDutchType_10",
    "NonDutchType_11",
    "NonDutchType_12",
    "NonDutchType_13",
    "NonDutchType_14",
    "NonDutchType_15_TEXT",
    "date",
    "time.0",
    "LocationLatitude",
    "LocationLongitude"
  )
  
  names.a <- c(names.m, "keyInteraction_1", "keyInteractionTime")

# Create reduced data sets for morning and afternoon
  dat.mo <- dtWorker$raw.morning[, names.m]
  dat.mo$daytime <- "morning"
  
  dat.af <- dtWorker$raw.afternoon[, names.a]
  dat.af$daytime <- "afternoon"

# merge morning and afternoon measurements with indicator [+ clean up]
  daily.dat <- rbind.fill(dat.mo, dat.af)
  daily.dat <- daily.dat[daily.dat$ExternalReference != 55951, ]
  dtWorker$daily <- daily.dat
  rm(dat.mo, dat.af, names.m, names.a, daily.dat)


# names for pre-measurement
  names.pre <- c(
    "Finished",
    "age",
    "Gender",
    "Living",
    "roommate_1",
    "roommate_2",
    "roommate_3",
    "nationality",
    "SecondNationality",
    "timeNL_1",
    "Reason_2",
    "Reason_5",
    "Reason_7",
    "Reason_8_TEXT",
    "DutchLang",
    "occupation_1",
    "occupation_2",
    "occupation_3",
    "occupation_4",
    "occupation_7",
    "CurrentEducation_1",
    "education_level",
    "EduLang_2",
    "RUG_faculty",
    "Study.0",
    "association",
    "DutchMeetNum",
    "DutchFriends_1",
    "assimilation",
    "separation",
    "integration",
    "marginalization",
    "VIA_heritage",
    "VIA_Dutch",
    "SSAS_surrounding",
    "SSAS_privat",
    "SSAS_public",
    "autonomy",
    "relatedness",
    "competence",
    "anxiety",
    "swl",
    "alertness",
    "calmness",
    "valence",
    "date",
    "time",
    "City",
    "ZIP",
    "id"
  )
  
# reduced data set for pre measurement
  dat.pre.red <- dtWorker$raw.pre[, names.pre]

# merge with daily data [+ clean up]
  df.pre <- merge(
    x = dtWorker$daily,
    y = dat.pre.red,
    by.x = "ExternalReference",
    by.y = "id",
    all = T
  )
  rm(names.pre)

# adjust duplicate names to fit to indicate daily or pre measurement  
  names(df.pre) <- gsub("[[:punct:]]x", ".daily", names(df.pre))
  names(df.pre) <- gsub("[[:punct:]]y", ".pre", names(df.pre))

# names for post measurement  
  names.post <- c(
    "ExternalReference",
    "assimilation",
    "separation",
    "integration",
    "marginalization",
    "VIA_heritage",
    "VIA_Dutch",
    "anxiety",
    "swl",
    "rosenberg",
    "social_support",
    "stress",
    "discrimination",
    "discrimination_month",
    "NLE_1month",
    "NLE_6month",
    "NLE_12month"
  )

# reduced data set for post-measurement  
  dat.post.red <- dtWorker$raw.post[, names.post]

# merge post measurement with pre- and daily data  
  df <- merge(
    x = df.pre,
    y = dat.post.red,
    by.x = "ExternalReference",
    by.y = "ExternalReference",
    all = T
  )

# adjust duplicate names to indicate pre or post  
  names(df) <- gsub("[[:punct:]]x", ".pre", names(df))
  names(df) <- gsub("[[:punct:]]y", ".post", names(df))
  
# add to list
  dtWorker$combined <- df
  
# create data frame with cleaned data
  df <- dtWorker$combined %>%
    filter(Finished.pre == 1,
           Finished.daily == 1,
           !is.na(ExternalReference))

# add running number as measurement ID within participants   
  df$measureID = rowidv(df, cols = c("ExternalReference"))
  
  dtWorker$clean <- df
  
# clean up
  rm(df.pre, names.post, dat.post.red, dat.pre.red, df)

# Export reduced Data
  #write.csv(dtWorker$clean, "data/processed/MT_clean-merged_07-05-2018.csv", row.names = F)
  #save(dtWorker$clean, file = "data/processed/MT_clean-merged_07-05-2018.RData")
```

```{r cleanStudents}
# our own test IDs
ownIDs <- c(
  "beautifulLionfishXXXR5rcgVBzGu8hPvOqrK8UBJBw4owvi9nfRFSFu3lMzYhE",
  "niceDogoXXXmB8JI5SFu78SF3DVof84mGUPPNUr14p2HYFTtp31a6D1OwAzM6F-K",
  "amusedQuailXXXmhuc_fpTp8vPkMwDH1BzjaH1d1kHSO1bsPEfsnaEYk4WeVBfPi",
  "juwGAbtXX0_1kmZtSVqKh3PGaHOICqUyU4iBkrT3nDsI_uifuD1gzKcZerxaM5FL"
)

# Prepare dfs for Cleaning
df.pre <- dtStudents$raw.pre %>%
  mutate_all(na_if,"") %>%
  mutate_all(na_if,"NA") %>%
  filter(!is.na(ended)) %>% # remove all who did not finish
  filter(!e_mail %in% .$e_mail[duplicated(.$e_mail)]) %>% # remove all who did the pre questionnaire multiple times (b/c inconsistent ratings scales)
  filter(!session %in% ownIDs) %>% # remove our own test 
  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)

df.post <- dtStudents$raw.post %>%
  mutate_all(na_if,"") %>%
  mutate_all(na_if,"NA") %>%
  filter(!is.na(session)) %>% # remove own test runs
  filter(!session %in% ownIDs) %>% # remove our own test 
  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
  filter(!is.na(ended)) %>% # remove all who never finished
  filter(!session %in% .$session[duplicated(.$session)]) %>% # remove all duplicate sessions
  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)

df.daily <- dtStudents$raw.daily %>%
  mutate_all(na_if,"") %>%
  mutate_all(na_if,"NA") %>%
  filter(!session %in% ownIDs) %>% # remove our own test 
  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
  filter(!is.na(ended)) %>% # remove all who never finished
  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)

# merge daily with pre
dfPreDaily = merge(
  x = df.daily,
  y = df.pre,
  by = "session",
  suffixes = c(".daily", ".pre"),
  all = F
)
  
# merge daily with post 
dfCombined = merge(
  x = dfPreDaily,
  y = df.post,
  by = "session",
  suffixes = c(".pre", ".post"),
  all = F
)

# add to list
dtStudents$clean <- dfCombined

# clean up workspace
rm(df.pre, df.daily, df.post, dfPreDaily, dfCombined, ownIDs)
```

```{r cleanMedical}
#TBD
```

## Calculate needed transformations  

```{r newVarsWorkers}
# ID variables
  short <- dtWorker$clean %>%
    mutate(
      PID = as.numeric(factor(ExternalReference)), # participant ID
      TID = measureID-1, # time ID with t0 = 0 for meaningfull intercept interpretations
      date = substr(StartDate,1,10), # awkward way of extracting date (best converted to )
      time = substr(StartDate,12,19), # awkward way of extracting time
      daynum = as.numeric(factor(date)), # all days as numeric for ordering
      daycor = ifelse(daytime=="morning" & period_to_seconds(hms(time))<period_to_seconds(hms("12:00:00")) | daytime=="afternoon" & period_to_seconds(hms(time))<period_to_seconds(hms("19:00:00")),daynum-1,daynum), # correctly identify which date the questionnaire is about
      daycor.lead = sprintf("%02d", daycor),
      daytime.lt = ifelse(daytime=="morning","a","b"), # morning / afternoon to a / b 
      day_time = paste(daycor.lead, daytime.lt, sep="_"), # combine day id with morning / afternoon
      session = as.numeric(factor(day_time)) # day and time identifier as numeric id
    )
  
  
  df <- dtWorker$clean
  
  df$PID = as.numeric(factor(df$ExternalReference)) # participant ID
  df$TID = df$measureID-1 # time ID with t0 = 0 for meaningful intercept interpretations
  
# Time and Date Variables: Correct morning / afternoon date where survey was collected the day after to indicate the correct date that was targeted
  df$SubTime = chron::times(df$time.0)
  df$SubTime[df$daytime == "afternoon"] = paste0(substring(as.character(df$time.0[df$daytime == "afternoon"]),4,8),":00")
  
  df$PPDate = as.Date(df$date.daily)
  df$PPDate[df$SubTime < "11:50:00" & df$daytime == "morning"] = df$PPDate[df$SubTime < "11:50:00" & df$daytime == "morning"]-1
  df$PPDate[df$SubTime < "18:50:00" & df$daytime == "afternoon"] = df$PPDate[df$SubTime < "18:50:00" & df$daytime == "afternoon"]-1
  
  df$time.daily = as.character(df$time.daily)
  df$time.daily[df$daytime == "afternoon" & !is.na(df$time.daily!="<NA>")] = paste0(substring(as.character(df$time.daily[df$daytime == "afternoon" & !is.na(df$time.daily!="<NA>")]),4,8),":00")
  
# Mood scales
  df$calmness.daily = rowSums(df[, c("calmness1", "calmness2")], na.rm = T)
  df$alertness.daily = rowSums(df[, c("alertness1", "alertness2")], na.rm =T)
  df$valence.daily = rowSums(df[, c("valence1", "valence2")], na.rm = T)
  
# Need scales
  df$keyMotiveFulfilled = rowSums(df[,c("keymotive_fulfillemt_1","keyMotive_noInt_fulf_1")], na.rm=T)
  df$autonomy.daily.all = rowSums(df[,c("autonomy_1","autonomy_NoInt_1")], na.rm=T)
  df$competence.daily.all = rowSums(df[,c("competence_1","competence_NoInt_1")], na.rm=T)
  #cor(df$relatedness_other_1, df$relatedness_self_1,use="complete.obs")
  df$relatedness.daily.all = rowMeans(df[,c("relatedness_other_1","relatedness_self_1","relatedness_1_NoInt_1")], na.rm=T)

# summarize by participant
  df$number[is.na(df$number)] = 0
  df$NonDutchNum[is.na(df$NonDutchNum)] = 0
  count = aggregate(list(CtContactNL=df$Contact_dum,
                         CtContactNonNl=df$inNonDutch,
                         CtContactNLAll=df$number,
                         CtContactNonNlAll=df$NonDutchNum), 
                    by=list(ExternalReference=df$ExternalReference), 
                    FUN=sum)
  average = aggregate(list(AvKeyNeed=df$keyMotiveFulfilled,
                           AvKeyNeedInt=df$keymotive_fulfillemt_1,
                           AvKeyNeedNoInt=df$keyMotive_noInt_fulf_1,
                           AvAutonomy=df$autonomy.daily.all,
                           AvCompetence=df$competence.daily.all,
                           AvRelatedness=df$relatedness.daily.all,
                           AvThermo=df$thermometerDutch_1,
                           AvWB=df$ExWB_1),
                      by=list(ExternalReference=df$ExternalReference), 
                      FUN=mean, na.rm=T)
  
  
  df.btw = df[,-c(9:162)]
  df.btw = df.btw[,-grep(names(df.btw),pattern="daily|ID|keyMotive")]
  
  df.btw = Reduce(function(x, y) merge(x, y, by="ExternalReference", all=TRUE), list(df.btw, count, average))
  df.btw = df.btw[!duplicated(df.btw$ExternalReference),]
  
  df.btw[!is.na(df.btw$assimilation.post),]
  
  df.btw$CtContactNL_c = scale(df.btw$CtContactNL, scale = FALSE)
  df.btw$AvKeyNeedInt_c = scale(df.btw$AvKeyNeedInt, scale = FALSE)
  df.btw$AvKeyNeed_c = scale(df.btw$AvKeyNeed, scale = FALSE)
  df.btw$CtContactNL_z = scale(df.btw$CtContactNL, scale = T)
  df.btw$AvKeyNeedInt_z = scale(df.btw$AvKeyNeedInt, scale = T)
  df.btw$AvKeyNeed_z = scale(df.btw$AvKeyNeed, scale = T)
  
  .GlobalEnv$df.btw = df.btw
  
  save(df.btw, file = "data/processed/df.btw.RData")  
  #write_sav(df.btw, "data/processed/MT_clean-merged_pre-post.sav")
  
# export data to Mplus

  df.mplus = remove_all_labels(select(df, PID, session, thermometerDutch_1, inNonDutch, Contact_dum, keyMotiveFulfilled, autonomy.daily.all, competence.daily.all, relatedness.daily.all))
  names(df.mplus)= c("PID", "session", "att", "intin", "intout", "keymot", "aut", "comp", "rel")
  mplus = df.mplus[order(df.mplus$PID, df.mplus$session),]
  mplus.intcont = mplus[mplus$intout==1,]
  prepareMplusData(mplus.intcont, "data/processed/dynamic-subset-intonly.dat")

```





# **Software Information**  
The full session information with all relevant system information and all loaded and installed packages is available in the collapsible section below.  

<details>
  <summary>System Info</summary>
  
  \renewcommand{\arraystretch}{0.8} <!-- decrease line spacing for the table -->
```{r Reproducibility-SessionInfo-R-environment, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center", out.width='100%', results='asis'}
  df_session_platform <- devtools::session_info()$platform %>% 
    unlist(.) %>% 
    as.data.frame(.) %>% 
    rownames_to_column(.)
  
  colnames(df_session_platform) <- c("Setting", "Value")
  
  kbl(
    df_session_platform, 
    booktabs = T, 
    align = "l",
    caption = "R environment session info for reproducibility of results" # complete caption for main document
  ) %>% 
    kable_classic(full_width = F, 
                  lightable_options = "hover", 
                  html_font = "Cambria") 
```
  \renewcommand{\arraystretch}{1} <!-- reset row height/line spacing -->
 </details>
 <br>
 <details>
  <summary>Package Info</summary>

\renewcommand{\arraystretch}{0.6} <!-- decrease line spacing for the table -->
```{r Reproducibility-SessionInfo-R-packages, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center", out.width='100%', results='asis'}
df_session_packages <- devtools::session_info()$packages %>% 
  as.data.frame(.) %>% 
  filter(attached == TRUE) %>% 
  dplyr::select(loadedversion, date, source) %>% 
  rownames_to_column

colnames(df_session_packages) <- c("Package", "Loaded version", "Date", "Source")

kbl(
  df_session_packages, 
  booktabs = T, 
  align = "l",
  caption = "Package info for reproducibility of results" # complete caption for main document
) %>% 
  kable_classic(full_width = F, 
                  lightable_options = "hover", 
                  html_font = "Cambria") 
```
\renewcommand{\arraystretch}{1} <!-- reset row height/line spacing -->
</details>
<br>
<details>
  <summary>Full Session Info (including loaded but unattached packages --- for troubleshooting only)</summary>
    `r pander(sessionInfo(), compact = FALSE)`
</details>


--------------------------------------------------------------------

</br>  

# **References**  

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>

